---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# scriptsearch

<!-- badges: start -->
<!-- badges: end -->

Scriptsearch is a package for searching R scripts you have previously made, but haven't documented. This is intended to help students look back at their old work and enable them to reuse the solutions they have already learned.

## Installation

You can install the released version of scriptsearch from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("scriptsearch")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("carlos-r-git/scriptsearch")
```
## Example

The function `scriptsearch` lists all files in a directory that contain specified search terms.

```{r example}
library(scriptsearch)

scriptsearch(dir = ".", searchterms = "search")
```

`showlines` can then be used on the output of `scriptsearch` to show all lines containing hits from the n^th^ file in the list.

```{r example2}
library(scriptsearch)

data <- scriptsearch(dir = ".", searchterms = "search")

showlines(data = data, n = 1)
```
