---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# scriptsearch

<!-- badges: start -->
<!-- badges: end -->

Scriptsearch is a package for searching R scripts you have previously made, but forgot to document. This is intended to help students look back at their old work and enable them to reuse solutions they have already learned.

## Installation

(Coming soon) You can install the released version of scriptsearch from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("scriptsearch")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("carlos-r-git/scriptsearch")
```
## Example

The function `scriptsearch` lists all files in a directory that contain specified search terms.

```{r example}
library(scriptsearch)

scriptsearch(dir = ".", searchterms = "search")
```

`showlines` can then be used on the output of `scriptsearch` to show all lines containing hits from the n^th^ file in the list.

```{r example2}
library(scriptsearch)

data <- scriptsearch(dir = ".", searchterms = "search")

showlines(data = data, n = 1)
```

## scriptsearch

```{r arguments, echo = FALSE}

table1 <- data.frame("Argument" = c("dir", "searchterms", "rm", "filetypes"),
                     "Default"  = c("N/A", "N/A", "TRUE", ".R, .Rmd"),
                     "Function" = c("Path of the directory", "Strings to search for", "Remove files with no hits from output", "Strings to be recognised in file names"),
                     "Example"  = c("\"./scripts\"", "c(\"text1\", \"text2\")", "TRUE", ".R, .Rmd"))

table1 %>% 
  knitr::kable()

```

## showlines

```{r arguments2, echo = FALSE}

table2 <- data.frame("Argument" = c("data", "n", "open"),
                     "Default"  = c("N/A", "N/A", "TRUE"),
                     "Function" = c("Table containing files and searchterms", "Row number of the file to be searched", "Open selected file"),
                     "Example"  = c("data <- scriptsearch(\"./scripts\", \"text\")", "1", "TRUE"))

table2 %>% 
  knitr::kable()

```
