---
title: "Scriptsearch Testing"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Scriptsearch-testing}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = system.file("extdata/testing", package = "scriptsearch"))
library(scriptsearch)
```
<br><br>

## What is Scriptsearch for?

Scriptsearch is an R package intended to help students search through their previous work. Poorly documented code can be hard to look back on, preventing you from reusing the solutions you've already written. This package contains two functions to help you search through your scripts. The source code can be found on github at https://github.com/carlos-r-git/scriptsearch.
<br><br><br>
This set of exercises is intended to show off the features of the package and how they can be used. The exercises can be completed by typing commands into the console or by making a new R script and running the commands line by line. At the end of this document is a link to a google form where you are welcome to give any feedback relating to the package.

<br>

## Installation

The scriptsearch package contains a folder of example scripts that will be used in these exercises. These files can be found in the path produced by `system.file("extdata/testing", package = "scriptsearch")`

```{r files, echo = TRUE}

fpath <- system.file("extdata/testing", package = "scriptsearch")

list.files(fpath)

```

<br>

## Exercises

### 1) Find example files

The function `scriptsearch()` defaults to searching the present working directory, so you will need to set the argument `dir` to match the path containing the example files (alternatively you can set your working directory to the folder containing the example files). Check that you can find the files with `list.files()` 
<br><br>
<details>
<summary> Click to reveal answer </summary>
<p>

```{r answer1, echo = TRUE}

fpath <- system.file("extdata/testing", package = "scriptsearch")

list.files(fpath)

```

</p>
</details> 
<br><br>

### 2) Searching

Let's search for some text in the example R scripts. `scriptsearch()` takes 4 arguments:

1) `searchterms` - Text you will search for in the target files

2) `dir` - Path to directory containing target files

3) `rm` - Logical for removing files with no hits from the output

4) `filetypes` - File endings used to filter target files

Arguments 2,3,4 have default values, however `searchterms` must always be supplied manually. Make sure to use `library(scriptsearch)` so that the scriptsearch functions are available.
<br><br><br>
`scriptsearch("text", dir = fpath)` will take "text" as the value for `searchterms` and search in `fpath` for .R and .Rmd files that contain the word `text`. 
<br><br><br>
Use `scriptsearch()` to search for the function "t.test" and see which files show up. Which argument would you change so that files which don't contain "t.test" also appear in the output?
<br><br>
<details>
<summary> Click to reveal answer </summary>
<p>

```{r answer2.0, eval = TRUE, echo = FALSE}

fpath <- "."

```

```{r answer2.1, eval = TRUE, echo = TRUE}

scriptsearch("t.test", dir = fpath, rm = FALSE)

```

</p>
</details> 
<br>

The default value for `filetypes` selects for .R and .Rmd files. What would you enter for `filetypes` so that only the "exampleprac.Rmd" files would be searched?
<br><br>
<details>
<summary> Click to reveal answer </summary>
<p>

```{r answer2.2, echo = TRUE}

scriptsearch("t.test", dir = fpath, filetypes = "Rmd", rm = FALSE)

```

</p>
</details> 
<br><br>

### 3) Opening files

We can now use the `showlines()` function to find where the "t.test" hits were. `showlines()` takes the output of `scriptsearch()` as its input. There are several ways to achieve this:

1) Assign the output of `scriptsearch()` to an object using `<-` and use `showlines()` on that object

2) Pipe the output of `scriptsearch()` into `showlines()` using ` %>% ` (requires `library(magrittr)` or `library(tidyverse)`)

3) Nest the `scriptsearch()` function inside `showlines()`

<br><br>
Use `showlines()` to find where "t.test" appears in the file `exampleprac5.R` (It may help to use the scriptsearch function first to find the index of the file you want to check)
<br><br>
<details>
<summary> Click to reveal answer </summary>
<p>

```{r answer3.1, echo = TRUE}

data <- scriptsearch("t.test", dir = fpath, rm = FALSE)
data

```

```{r answer3.2, eval = FALSE, echo = TRUE}

showlines(data, 12)

```

```{r answer3.3, echo = FALSE}

showlines(data, 12, open = FALSE)

```

Alternative methods:

```{r answer3.4, eval = FALSE, echo = TRUE}

scriptsearch("t.test", dir = fpath, rm = FALSE) %>% showlines(., 12)

showlines(scriptsearch("t.test", dir = fpath, rm = FALSE), 12)

```

</p>
</details> 
<br><br>

### 4) Reading the output

Once the output of `scriptsearch()` is in an object it can be read just like any other data frame. 
<br><br><br>
Can you find the total number of times "ggplot" appears in the example scripts? 

Which file contains "ggplot" the most?
<br><br>
<details>
<summary> Click to reveal answer </summary>
<p>

```{r answer4.1, echo = TRUE}

data <- scriptsearch("ggplot", dir = fpath)

# total "ggplot"
sum(data$Hits)

# file with most "ggplot"
data$Path[which.max(data$Hits)]

```

</p>
</details> 
<br><br>

### 5) No hits found?

What happens if you search for a string which does not appear in any of the files? Try searching for a long nonsense string with and without `rm = FALSE`. 
<br><br>
<details>
<summary> Click to reveal answer </summary>
<p>

```{r answer5.1, echo = TRUE}

scriptsearch("zzzz")
scriptsearch("zzzz", rm = FALSE)

```

</p>
</details>
<br>

Now try using `showlines()` to read a file which didn't contain any hits (you will need to use `rm = FALSE` for `scriptsearch()`). 
<br><br>
<details>
<summary> Click to reveal answer </summary>
<p>

```{r answer5.2, echo = TRUE}

no_files <- scriptsearch("zzzz") 
showlines(no_files, 1)

no_hits <- scriptsearch("zzzz", rm = FALSE)
showlines(no_hits, 1)

```

</p>
</details>

<br>

## Feedback

Please find below a short google form (5 questions) where you can send feedback relating to scriptsearch:

[Link to form](https://docs.google.com/forms/d/e/1FAIpQLScj6yDxY8wP5VOwUZMjq8GV534ZpMn9JkpdEfDl_uFw1fHL1A/viewform?usp=sf_link)

Thanks for testing scriptsearch!
